Starcode tutorial

### 2015-11-17 doc/tutorial.tex

The previous example is a standard invocation of Starcode on sequence
data. The input file \texttt{test/test\char`_file.txt} is in raw format
(\textit{i.e.} plain text), it contains 35 lines, each with one
sequence of 20 nucleotides. By default, Starcode is verbose and prints
some information about the clustering process. In the example above,
Starcode used a single CPU, and it clustered the sequences within
edit distance 2 of each other.

The output starts after the line \texttt{progress: 100.00\%}. It
consists of five lines (one per cluster) where the sequence is the
centroid of the cluster (the most representative sequence) and the
number is its size (the number of sequences in the cluster).

>>>>

Starcode is a sequence clustering algorithm. It takes a bunch of
sequences, finds which are similar and pools them together. Starcode
considers that two sequences are similar if their edit distance
(also known as the Levenshtein distance) is low, \textit{i.e.}
if they almost identical, except for a few mismatches, insertions
and deletions.

The previous example is a standard run of Starcode on sequence
data. By default, Starcode is verbose and gives some information on
how the run is performed before it outputs the clusters. 
In this case, we learn that Starcode used a single CPU, that
the input file \texttt{test/test\char`_file.txt} is in raw format
(\textit{i.e.} plain text), and that the threshold distance for
similarity search was set to 2. The output propoer starts after
the line \texttt{progress: 100.00\%}. It consists of five lines
(one per cluster) where the sequence is the centroid of the cluster
(the irepresentative sequence) and the number is its size (the
number of sequences in the cluster).

The input file \texttt{test/test\char`_file.txt} contains 35 sequences
that Starcode arranged in 5 clusters of 7 sequences each.
